|

### 2019-12-26 inst/manuscript/candidaev_figures.Rmd
Address reviewer 2 comment 3
Figure 1B hard to read because ATCC10231 particle concentration a lot
lower than the others.

Changed Figure 1B to percentage of total bar chart which shows
differences in size distribution better. Old Figure 1B should be
moved to supplementary material.

# construct figure 1b
f1b <- nta_bioavg %>% 
  ggplot(aes(x = particle_size, y = Bio_rep_mean, colour = Strain)) + 
  scale_colour_manual(values = st_pal[c(3, 2, 4, 1)], 
                      breaks = c("DAY286", "ATCC90028", 
                                 "ATCC10231", "Biofilm"), 
                      labels = c("DAY286 Y", "ATCC90028", 
                                 "ATCC10231", "DAY286 B")) + 
  geom_vline(xintercept = 100, colour = "#999999", linetype = "dashed") +
  geom_line(size = 0.5) + 
  facet_wrap(~ facet, scales = "free", ncol = 2, nrow = 1) + 
  theme_classic() + 
  theme(strip.background = element_blank(), 
        strip.text = element_blank(), 
        legend.position = c(0.88, 0.6), 
        legend.title = element_blank(), 
        plot.margin = margin(t = 0.2, l = 0, r = 0.2, b = 0, unit = "inches"), 
        axis.text.x = element_text(colour = "black")) + 
  xlab(label = "Particle size (nm)") + 
  ylab(label = "Particles / mL")

@@

f1c <- nta_total %>% 
  ggboxplot(x = "Strain", y = "part_per_prot", 
            color = "Strain", palette = st_pal, add = "jitter", 
            add.params = list(color = "black"), 
            shape = 15,
            ylab = expression("Particles /"~paste(mu,g)~"protein"))
f1c <- ggpar(f1c, 
             yscale = "log10", 
             format.scale = TRUE, 
             ylim = c(8e8, 8e10),
             font.y = 10, 
             legend = "none") + 
  stat_pvalue_manual(nta_total_tukey[c(2,4,6), ], label = "p.adj", 
                     y.position = c(10.45, 10.65, 10.85), 
                     tip.length = 1e-2, 
                     label.size = 3) + 
  theme(axis.title.x = element_blank(), 
        plot.margin = margin(t = 0.2, l = 0.2, r = 0, b = 0.15, 
                             unit = "inches")) + 
  scale_x_discrete(labels = c("ATCC90028" = "A9", 
                              "ATCC10231" = "A1", 
                              "Biofilm" = "B", 
                              "DAY286" = "Y"))

>>>>

# construct figure 1b
nta_binned <- nta_techavg %>% 
  ungroup() %>% 
  mutate(bin = ntile(particle_size, 10)) %>% 
  nanocount(Strain, Bio_rep, bin, 
            param_var = Tech_rep_mean)

test <- nta_binned %>% 
  mutate(bin = as.factor(bin))

test2 <- aov(Particle_count ~ Strain * bin, data = test)
summary(test2)

TukeyHSD(test2, which = "Strain")

nta_binned_bio <- nta_binned %>% 
  nanolyze(Strain, bin, 
           name = "Bio_rep", 
           param_var = Particle_count)

nta_percent <- nta_binned_bio %>% 
  group_by(Strain) %>% 
  summarise(Total_particles = sum(Bio_rep_mean)) %>% 
  left_join(nta_binned_bio, by = "Strain") %>% 
  select(-Total_particles, Total_particles) %>% 
  mutate(Percentage_total = Bio_rep_mean / Total_particles * 100, 
         Percentage_se = Bio_rep_se / Total_particles * 100) %>% 
  filter(bin %in% c(1, 2, 3, 4, 5, 6))

nta_percent$Strain <- factor(nta_percent$Strain, 
                             levels = c("DAY286", "ATCC90028", 
                                        "ATCC10231", "Biofilm"))

f1b_x_labs <- c("0-100", "100-200", "200-300", "300-400", "400-500", "500-600")

f1b <- ggplot(data = nta_percent, aes(x = as.factor(bin), 
                               y = Percentage_total, 
                               fill = Strain)) + 
  geom_bar(stat = "identity", position = "dodge") + 
  geom_errorbar(aes(ymin = Percentage_total - Percentage_se, 
                    ymax = Percentage_total + Percentage_se), 
                width = 0.2, 
                position = position_dodge(0.9)) + 
  scale_fill_manual(values = st_pal) + 
  scale_x_discrete(labels = f1b_x_labs) + 
  labs(x = "Particle size (nm)", 
       y = "% of total particles   ") + 
  theme_classic() + 
  theme(legend.position = c(0.8, 0.6), 
        axis.text = element_text(colour = "black"), 
        legend.title = element_blank())

@@

f1c <- nta_total %>% 
  ggboxplot(x = "Strain", y = "part_per_prot", 
            color = "Strain", palette = st_pal, add = "jitter", 
            add.params = list(color = "black"), 
            shape = 15,
            ylab = expression("Particles /"~paste(mu,g)~"protein"))
f1c <- ggpar(f1c, 
             yscale = "log10", 
             format.scale = TRUE, 
             ylim = c(8e8, 8e10),
             font.y = 10, 
             legend = "none") + 
  stat_pvalue_manual(nta_total_tukey[c(2,4,6), ], label = "p.adj", 
                     y.position = c(10.45, 10.65, 10.85), 
                     tip.length = 1e-2, 
                     label.size = 3) + 
  theme(axis.title.x = element_blank(), 
        plot.margin = margin(t = 0.2, l = 0.2, r = 0, b = 0.15, 
                             unit = "inches")) + 
  scale_x_discrete(labels = c("ATCC90028" = "A9", 
                              "ATCC10231" = "A1", 
                              "Biofilm" = "B", 
                              "DAY286" = "Y")) + 
  coord_cartesian(clip = "off")
